---
title: "ggplot2"
author: "Chia-Yu Wei"
date: "2023-11-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ggplot2
The package which is useful and popular to be used on data visualization.
```{r}
library(ggplot2)
```

### Data (no plot shown yet)
```{r}

ggplot(data = mtcars) 
```

### Data and Aesthetics
```{r}
ggplot(data = mtcars, aes(x = mpg, y = hp))
```

### Data, Aesthetics, and Geometries
```{r}
pl <- ggplot(data = mtcars, aes(x = mpg, y = hp))
pl + geom_point()
```

### Data, Aesthetics, Geometries, and Facets
```{r}
pl <- ggplot(data = mtcars, aes(x = mpg, y = hp)) +
  geom_point() 
pl + facet_grid(cyl ~ .)
```

### Data, Aesthetics, Geometries, Facets, and Statistics
```{r}
pl <- ggplot(data = mtcars, aes(x = mpg, y = hp)) +
  geom_point() 
pl + facet_grid(cyl ~ .) + stat_smooth()
```

### Data, Aesthetics, Geometries, Facets, Statistics, and Coordinates
```{r}
pl <- ggplot(data = mtcars, aes(x = mpg, y = hp)) +
  geom_point() 
pl2 <- pl + facet_grid(cyl ~ .) + stat_smooth()
pl2 + coord_cartesian(xlim = c(15, 25))
```

### Data, Aesthetics, Geometries, Facets, Statistics, Coordinates, and Theme
```{r}
pl <- ggplot(data = mtcars, aes(x = mpg, y = hp)) +
  geom_point() 
pl2 <- pl + facet_grid(cyl ~ .) + stat_smooth()
pl2 + coord_cartesian(xlim = c(15, 25)) + theme_bw()
```

\newpage
# Histograms
Here is a Rstudio cheat sheet  (https://statsandr.com/blog/files/ggplot2-cheatsheet.pdf)
Use: + geom_histogram()

```{r}
#install.packages('ggplot2movies')
library(ggplot2movies)
```
```{r}
# Data + Aesthetics
colnames(movies)
pl <- ggplot(movies, aes(x = rating))
```

```{r}
# Data + Aesthetics + Geometries
pl2 <- pl + geom_histogram(binwidth = 0.1,
                          color = 'black',
                          fill = 'red',
                          alpha = 0.3)
print(pl2)
# Alpha: transparency
```
### Adjusted Version (advanced)
```{r}
# Data + Aesthetics + Geometries
pl2_adj <- pl + geom_histogram(binwidth = 0.1,
                          aes(fill = ..count..))
print(pl2_adj)
# Alpha: transparency
```

```{r}
# Make it to center
(pl3 <- pl2 + xlab('Movie Rating') + ylab('Count') + ggtitle("My Title") + theme(plot.title = element_text(hjust = 0.5)))
```
\newpage
# Plot
```{r}
library(ggplot2)
df <- mtcars

# Data & Aesthetics
pl <- ggplot(df, aes(x = wt, y = mpg))

# Geometric
pl + geom_point(aes(size = cyl),  # The size changes with the 'cyl' data.
                col = 'blue',
                alpha = 0.5)
pl + geom_point(aes(size = factor(cyl)),  # The size changes with the 'cyl' data.
                col = '#006699',
                alpha = 0.5)

# factor() remove the category that we don't use.
```

### Shape
```{r}
# The shape and color changes with the 'cyl' data.
pl2 <- pl + geom_point(aes(size = hp, color = hp),
                       alpha = 0.8)
pl2 + scale_color_gradient(low = '#78fb5c', high = 'red')
```
Here is the link to ggplot color code:(https://redketchup.io/color-picker)

\newpage
# Boxplot
```{r}
df <- mpg

pl <- ggplot(df, aes(x = class))
pl + geom_bar(aes(fill = drv))
```
```{r}
pl + geom_bar(aes(fill = drv), position = "dodge")
```
```{r}
pl + geom_bar(aes(fill = drv), position = "fill")
```

\newpage
# Boxplots
```{r}
df <- mtcars
# X value should not be continuous vale, it should be category variable,
pl <- ggplot(df, aes(x = factor(cyl), y = mpg))
pl + geom_boxplot(fill = 'pink')
```
```{r}
pl + geom_boxplot(aes(fill = factor(cyl))) + theme_dark()
```
```{r}
# Flip the coordinate
pl + geom_boxplot() +coord_flip()
```