---
title: "Capstone Data Project"
author: "Chia-Yu Wei"
date: "2023-2-15"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data
We use the data from [Sean Lahaman's Website](http://www.seanlahman.com/baseball-archive/statistics/). It's a useful score for baseball statistics.
```{r}
# Import data
batting <- read.csv('batting.csv')
head(batting)
```
It's a data with 24 variables.   
```{r}
str(batting)
```

### Let's create the new statistic! For example, for Batting Average, here's the formula for batting average:
$$
AVG = \frac{H}{AB}
$$
 
Which means that the Batting Average is equal to H (Hits) divided by AB (At Base). So we'll do the following to create a new column called **BA** and add it to our data frame:
```{r}
batting$AVG <- batting$H / batting$AB
tail(batting$AVG)
```

### Now, calculate On Base Percentage (OBP) and Slugging Percentage (SLG).
```{r}
#On Base Percentage
attach(batting)
batting$OBP <- (H + BB + HBP) / (AB + BB + HBP + SF)
```
```{r}
batting$X1B <- H - X2B - X3B - HR

#Slugging Percentage
batting$SLG <- ((1 * batting$X1B) + (2 * X2B) + (3 * X3B) + (4 * HR)) / AB
```
```{r}
str(batting)
```

\newpage
## Merging Salary Data with Batting Data
Let's merge data about salary with the player data above.
```{r}
salary <- read.csv('Salaries.csv')
head(salary)
```
Since our salary data starts from 1985 but batting data is starting from 1871, we should select the data after 1985.
```{r}
batting <- subset(batting, yearID >= 1985)
summary(batting)
```

### Let's merge the salary data and batting data.
```{r}
combo <- merge(batting, salary, by = c('playerID', 'yearID'))
head(combo)
```

\newpage
## Analyzing the Lost Player
From story about *The 2022 Oakland A's*, the Oakland A's lost 3 key players during the off-season. We'll want to get their stats to see what we have to replace. The players lost were: first baseman 2000 AL MVP Jason Giambi (giambja01) to the New York Yankees, outfielder Johnny Damon (damonjo01) to the Boston Red Sox and infielder Rainer Gustavo "Ray" Olmedo ('saenzol01').

### Use the subset() function to get a data frame called lost_players from the combo data frame consisting of those 3 players. Hint: Try to figure out how to use %in% to avoid a bunch of or statements!
```{r}
lost_player <- subset(combo,
                      playerID %in% c('giambja01','damonjo01','saenzol01'))


#44x31
dim(lost_player)
```

We only get the data which yearID is 2001, and reduce the variables to what we need.
```{r}
lost_player <- subset(lost_player, yearID == 2001)
new_lost <- lost_player[, c('playerID', 'H', 'X2B', 'X3B', 'HR', 'OBP', 'SLG', 'AB')]
head(new_lost)
```

\newpage
## Task
Now we have all the information we need! Here is your final task - Find Replacement Players for the key three players we lost! However, you have three constraints:

- The total combined salary of the three players can not exceed 15 million dollars.

- Their combined number of At Bats (AB) needs to be equal to or greater than the lost players(minimum is 520 in lost platers)
).
- Their mean OBP had to equal to or greater than the mean OBP of the lost players
```{r}
library(dplyr)
library(ggplot2)
avail.players <- filter(combo, yearID == 2001)
ggplot(avail.players, aes(x = OBP, y = salary)) + geom_point()
```
```{r}
avail.players <- filter(avail.players, salary < 8000000, OBP > 0, AB >= 520)
candidate <- head(arrange(avail.players,desc(OBP)),10)
(possible <- candidate[,c('playerID','OBP','AB','salary')])
```
We select some players who is satisfied with our condition, and sort the data by *OBP*. The first choice is 'giambja01', but we can not choose him agian. Therefore, we should choose player rank2 to 4.
```{r}
possible[2:4, ]
```