---
title: "Project"
author: "Chia-Yu Wei"
date: "2023-12-04"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Correlation between corruption and development
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)
```

### Import the data from ggplot2
```{r}
# Name the data as 'df'
df <- fread("C:/Users/Chiayu/OneDrive/Desktop/Data Science and Machine Learning Bootcamp with R/Project/Economist_Assignment_Data.csv",
            drop = 1)
head(df)
```

## Relation between CPI and HDI
- Consumer Price Index (CPI) is a measure of the average change over time in the prices paid by urban consumers for a market basket of consumer goods and services.
- Human Development Index (HDI) 

```{r}
pl <- ggplot(
  df,
  aes(x = CPI, y = HDI, color = Region))
pl2 <- pl +
  geom_point(size = 3, shape = 1) + 
  theme_gray()
pl2
```

Now, we gonna create the linear regression line of the model y ~ log(x)
```{r}
# Make linear regression
pl3 <- pl2 + geom_smooth(aes(group = 1),
                  method = 'lm', 
                  formula = y ~ log(x),
                  se = FALSE,
                  color = 'red')
pl3
```

### Using *geom_text* to add text to the plot.
```{r}
pl3 + geom_text(aes(label = Country))
```

# Label some counties.
```{r}
Total_label <- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
                 "Afghanistan", "Congo", "Greece", "Argentina", "Brazil",
                 "India", "Italy", "China", "South Africa", "Spane",
                 "Botswana", "Cape Verde", "Bhutan", "Rwanda", "France",
                 "United States", "Germany", "Britain", "Barbados", "Norway",
                 "Japan", "New Zealand", "Singapore")
pl4 <- pl3 + geom_text(aes(label = Country),
                color = "gray20",
                data = subset(df, Country %in% Total_label),
                check_overlap = TRUE)
pl4
```
### Add limit to make the graph better to be watched.
```{r}
pl4 + theme_bw() + scale_x_continuous(name = 'Same x axis as the Economist Plot',
                                      limits = c(1, 10),
                                      breaks = 1:10)
```